How to compute the fusion product of MV cycles in type A

### 2021-02-24 draft.tex
mtg chgs begun to lunch break

@@

We will also study the affine space of $m\times m$ matrices which we denote $ M_m$.
% nicematrix test
% $\begin{bNiceArray}{ccc|c}[margin]
%     \Block{3-3}<\Large>{A} & & & 0 \\
%     & \hspace*{1cm} & & \Vdots \\
%     & & & 0 \\
%     \hline
%     0 & \Cdots& 0 & 0
%     \end{bNiceArray}$
% 
% $\begin{pNiceMatrix}
%     \frac12 & -\frac12 \\
%     \frac13 & \frac14 \\
%     \end{pNiceMatrix}$

@@

\subsection{Lattices}
\label{ss:lat}
We will use the lattice model, so it is useful to recall the following definition.  Let $ R \subset K$ be two rings (usually, but not always, $K$ will be a field \acom{When is $K$ not a field?}).  Let $ m \in \mathbb N$ \acom{we have already fixed $m$?} and consider $ K^m $ as a $K$-module.   By restriction $ K^m$ can be viewed as an $R$-module.  An $R$-lattice in $M$ \acom{what is $M$? should be $K^m$?} is an $R$-submodule $ L \subset K^m$ such that $ L $ is a free rank $ m $ $R$-module and $ L \otimes_R K = K^m $.  Equivalently, $ L = \Sp_R(v_1, \dots, v_m)$ where $v_1, \dots, v_m$ are free generators of $K^m$.

% The trivial lattice is 
$L_0(R) = R^m \subset K^m $ is called the standard lattice. The group $\GL_m(K) $ acts transitively on the set of $R$-lattices in $K^m$, thus giving a bijection between 
% the set of such lattices 
this set and $\GL_m(K)/\GL_m(R)$.

We will be particularly interested in $\CC[t]$-lattices in $ \CC(t)^m$.  Given such a lattice $ L $ and a point $ a \in \CC$, the specialization of $ L $ at $ a $ is defined as
$$
L(a) := L \otimes_{\CC[t]} \CC\xt[t-a] \subset \CC\xT[t-a]^m\,.
$$
We say that $ L $ is trivial at $ a $ if $ L(a) = \CC\xt[t-a]^m$. \acom{Do we want to employ the notation $\cO_a$ and $\cK_a$ here?}
For example, the lattice $(t-s)^{-1}\CC[t] \subset \CC(t)$ is trivial at any $a\ne s$.

@@

\subsection{Affine Grassmannians} %  actors

Set $\AA = \AA^1$ and $\PP = \PP^1$.

\begin{itemize}
    \item The ordinary affine Grassmannian $\Gr = G(\cK)/G(\cO)$. It is described in modular terms by 
    $$
    \Gr = \{ (P, \varphi) : \text{$V$ is a rank $m$ vector bundle on $ D_0 $, $\varphi : V \rightarrow V_0 $ on $ D_0 \setminus \{0\} $} \} 
    $$
    where $V_0$ is the trivial rank $m$ vector bundle, and $ D_0$ is the formal disk centered at $ 0 \in \PP$.

    We also have a lattice description 
    $$ 
    \Gr = \{ L \subset \cK^m : \text{ $L$ is a $\cO$-lattice} \}\,.
    $$
    % 
    \item For any $ s \in \CC $, \acom{should it be $\AA$ instead of $\CC$} the ordinary affine Grassmannian $\Gr_s = G(\cK_s)/G(\cO_s)$ at $ s $. It is described in modular terms by
    $$
    \Gr_s = \{ (P, \varphi) : \text{$V$ is a rank $m$ vector bundle on $ D_s $, $\varphi : V \rightarrow V_0 $ on $ D_s \setminus \{s\} $} \} 
    $$
    where $D_s$ is the formal disk centered at $s\in\PP$.

    We also have a lattice description 
    $$ 
    \Gr_s = \{ L \subset \cK_s^m : \text{ $L$ is a $\cO_s$-lattice} \} \,. 
    $$   
    \item The thick affine Grassmannian $\Grth = G(\Kinf)/G(\CC[t])$. % \CC\xT[t^{-1}]
    It is described in modular terms by
    $$
        \Grth = \{ (P, \varphi) : \text{$V$ is a rank $m$ vector bundle on $ \PP $, $\varphi : V \rightarrow V_0 $ on $ D_\infty $ } \} % (a disk centered at $ \infty$)
    $$
    where $D_\infty$ denotes a disk centered at $ \infty$. 
    % \acom{What is the difference between ``a disk'' and ``the formal disk''} \jcom{No difference.}

@@

    \jcom{Maybe write $\Kinf$ for $ \CC\xT[t^{-1}] $?  Also maybe change the ``thick'' notation''.} \acom{Since $\sf th$ is also the first two letters of ``thin''?} \jcom{That's a good point!  Maybe we could use some kind of bold  Gr (``thick'' letters) or maybe that would be too confusing.} \acom{Ok, it's tentative.}

    \item The (two point) Beilinson--Drinfeld Grassmannian $\pi : \Grbd\to \AA$ (with one point fixed at 0, and the second point $s\in\AA$ varying).
    It is described in modular terms by
    % {\small
    $$
    \Grbd = 
    % \begin{aligned}
        \left\{ 
            (V,\varphi,s) : V\text{ is a rank $m$ vector bundle on }\PP, \varphi : V \rightarrow V_0 \text{ on } \PP \setminus \{0, s\}  
        \right\} 
    % \end{aligned}
    $$%}

    The fibre of $\Grbd \to \AA$ over $ s \in \AA $, for $ s \ne 0$, will be denoted $ \Gr_{0,s} $ and is given by
    % 
    $$ 
    \Gr_{0,s} := \pi^{-1}(s) = G(\CC[t, t^{-1}, (t-s)^{-1}]/G(\CC[t])\,.
    $$
    % \acom{0 in notation is kinda redundant? But we can't take it away because we already have a $\Gr_s$ and it is something else?}
    % \jcom{Yes, that is one reason.  But also, there was a comment of yours before in the file, saying that you sometimes got confused that one point was fixed at 0, so this is a good notation to remind us (and the reader).  For the same reason, maybe we should write $ \Gr_{0, \AA}$ instead of $ \Gr_\AA$.}
    % \acom{lol}

    We also have a lattice descriptions 
    % {\small
    \begin{gather*}
    \Grbd = 
    \{ L \subset  \CC(t)^m, s \in \CC : \text{ $L$ is a $\CC[t]$-lattice 
    % , $L$ is 
    trivial at any $ a \ne 0, s$} \} \\
     \Gr_{0,s} = 
    \{ L \subset  \CC[t,t^{-1},(t-s)^{-1}]^m : \text{ $L$ is a $\CC[t]$-lattice} \}
    \end{gather*}%}
    \acom{$s\in\CC$ should be $s\in\AA$?}
    \jcom{Sorry I was very consistent about $ \CC$ vs $\AA$.  Which do you prefer?}
    % 
    \item The positive parts $ \Gr^+$ and ${\Grth}^+$ of the affine Grassmannian and of the thick affine Grassmannian resp.\ are defined as 
    % and of the thick affine Grassmannian ${\Grth}^+$ is defined as
    $$
    \Gr^+ = (M_m(\cO) \cap G(\cK)) / G(\cO) \quad {\Grth}^+ = (M_m(\CC[t]) \cap G(\Kinf) / G(\CC[t]) % \CC\xT[t^{-1}] missed a spot  
    $$
    % \acom{What is $M_m$?} \jcom{The space of matrices.  I added it to the beginning of section 2.}

@@

    In lattice terms, $ \Gr^+$ (resp. ${\Grth}^+$) contains those lattices $L$ which are contained in the standard 
    % \acom{previously called ``trivial''} \jcom{I changed it so that $ R^m $ is called the standard lattice.  But I would like to leave the terminology ``trivial at $ a$'' is that ok, or should we write ``standard at $a$''.} 
    % \acom{Oh, I don't know.. is trivialized at $a$? is standardized at $a$? Maybe standard at $a$ is better.. Man I never thought about this interchangeable lingo.} 
    lattice $ L_0(\cO)$ (resp. $L_0(\CC[t])$. % , i.e. $ L \subseteq L_0$.
\end{itemize}

These \acom{which?} different versions of the affine Grassmannian are related as follows.

First there is an isomorphism $ \Gr_s \cong \Gr $ coming from the isomorphism $ \cK \cong \Ks$.

Second, we have a map from the two point BD affine Grassmannian to the thick affine Grassmannian $ \Grbd \rightarrow \Grth $
% $$ \Grbd \rightarrow \Grth $$ 
which is given in modular terms by restricting the trivialization to $ D_\infty$.  It is given in group-theoretic terms on the fibre over $ s $ by
$$
G(\CC[t, t^{-1}, (t-s)^{-1}])/ G(\CC[t]) \rightarrow G(\Kinf)/G(\CC[t])
$$
% \acom{Permission to update notation and replace $\CC\xT[t^{-1}]$ by $\Kinf$ as per your suggestion Joel?}
% \jcom{Permission granted!}
% \acom{replaced}

Finally, it is given in lattice terms as the identity on the lattice and using the inclusion $\CC[t, t^{-1}, (t-s)^{-1}]^m \rightarrow \Kinf^m$ on the ambient spaces.

The fibres $ \Gr_{0,s}$ of $ \Grbd \rightarrow \AA$ can be described as % are given as follows
$$
\Gr_{0,s} \cong 
\begin{cases} 
    \Gr \times \Gr_s & s \ne 0 \\
    \Gr              & s = 0\,.
\end{cases}
$$
In the $s\ne 0$ case, the isomorphism is given in the modular realization by restricting the vector bundle and trivializating to the appropriate disks.  
In the lattice realization, it is given by forming tensor products 
$$
L \mapsto (L(0), L(s))\,.
$$
% in the $ s \ne 0 $ case.
\jcom{Maybe we should introduce some notation for this isomorphism.}
% \acom{Ok. Question: how is the isomorphism given at $s=0$?}
\acom{Ok. TODO.}

@@

\jcom{I tried to answer your question, but didn't explain it well.  When $ s = 0$, the map is the same except that $ L(0) = L(s) $ , so we only need $L(0)$.}

\subsection{The fusion construction}
The following construction will be very important in this paper.  Let $ X_1, X_2 \subset \Gr$ be two subschemes. Then using the isomorphism $ \Gr \cong \Gr_s $, for each $ s $, we obtain a subscheme $ X_1 \times X_2 \subset \Gr \times \Gr_s $.  
% <<<<<<< HEAD
% Via \ul{this} \acom{rather, the above? $L\mapsto (L(0),L(s))$} 
Next, using the isomorphism $ \Gr_{0,s} \cong \Gr \times \Gr_s $,  for each $ s \ne 0$, we obtain a subscheme $ X_1 \times X_2 \times \AA^\times $  of $\Grbd$.  
% =======
% Via the isomorphism $ \Gr_{0,s} \cong \Gr \times \Gr_s $,  for each $ s \ne 0$, we obtain a subscheme $ X_1 \times X_2 \times \AA^\times $  of $\Grbd$.  
% >>>>>>> 5a15ce15b14109bab482282aa5657c9596f7892d

@@

% 
\begin{itemize}
    % \item Weights $\mu_i\le\lambda_i$ of size $N_i$ ($i=1,2$) 
    % \item Their sums $\mu = \sum \mu_i \le \lambda = \sum\lambda_i$ of size $N = \sum N_i$
    \item The point $L_\lambda = t^\lambda G(\cO)$ in $\Gr$. In the lattice model, we have
    $$ 
    L_\lambda = \Sp_\cO(t^{\lambda_1}e_1, \dots, t^{\lambda_m}e_m)\,. 
    $$
    \item The orbit $\Gr^\lambda = G(\cO) L_\lambda$ and its closure 
    $ \overline\Gr^\lambda = \bigcup_{\lambda' \le \lambda} \Gr^{\lambda'} $.  
    \acom{do we prefer $\overline{\Gr}^\lambda$ to $\overline{\Gr^\lambda}$? I am for the former! Though it is less accurate??} \jcom{I'm not sure which is better.  I was ``testing'' it out.}
    This orbit lies inside the positive part $ \Gr^+$ of the affine Grassmannian.
    % 
    \item The family $ \overline{\Gr}_{0,\AA}^{\lambda_1, \lambda_2} \rightarrow \AA$ defined by $ \overline{\Gr}^{\lambda_1, \lambda_2}_{0, \AA} = \overline{\Gr}^{\lambda_1} \ast \overline{\Gr}^{\lambda_2}$. 
    % \acom{I guess that it is good to have the notation here, in place of $\overline{\overline\Gr^{\lambda_1}\times\overline\Gr^{\lambda_2}\times\AA^\times}$..}
    %\acom{should we also subsript this family with $0,\AA$?}

@@

    Suppose that $ s \ne 0$.  In the fibre $\overline{\Gr}_{0,s}^{\lambda_1, \lambda_2}$ we have the open locus $ \Gr_{0,s}^{\lambda_1, \lambda_2}$ coming from transporting $ \Gr^{\lambda_1} \times \Gr^{\lambda_2} $ via the isomorphism $ \Gr_{0,s} \cong \Gr \times \Gr_s $.  This open locus is a $ G(\CC[t])$-orbit
    % .  The lattice description of $ \Gr_{0,s}^{\lambda_1, \lambda_2}$ 
    whose lattice description is given in \Cref{le:Grl1l2} below.
    \acom{Why $G(\CC[t])$}

    \item The locus $\cW_\mu = G_1\xt[t^{-1}]L_\mu \subset \Grth $.  
    \acom{want $t^\mu\CC[t]$ as opposed to $L_\mu$ here?}
    In modular terms, this corresponds to the locus of those $ (V, \varphi)$ such that $ V $ is isomorphic to the trivial vector bundle on $ \PP$ and such that $ \varphi$ preserves the {Harder--Narasimhan filtration of $V$ at $ \infty$}.  The lattice description of $ \cW_\mu \cap \Grth^+$ is given in Lemma \ref{le:Wmu} below.

>>>>

\subsection{Rings and discs}

@@

Set $\PP = \PP^1$. We will study formal spectra of $R$ and $K$ as formal disks in $\PP$. \acom{TODO: talk about discs.}

\subsection{Groups}

We will also study the affine space of $m\times m$ matrices which we denote $ M_m$.

% nicematrix test
% $\begin{bNiceArray}{ccc|c}[margin]
%     \Block{3-3}<\Large>{A} & & & 0 \\
%     & \hspace*{1cm} & & \Vdots \\
%     & & & 0 \\
%     \hline
%     0 & \Cdots& 0 & 0
%     \end{bNiceArray}$
% 
% $\begin{pNiceMatrix}
%     \frac12 & -\frac12 \\
%     \frac13 & \frac14 \\
%     \end{pNiceMatrix}$

@@

\subsection{Lattices}
\label{ss:lat}
We will use the lattice model, so it is useful to recall the following definition. Let $ R \subset K$ be two rings (usually, but not always, $K$ will be a field 
% \acom{When is $K$ not a field?}). Let $ m \in \mathbb N$ \acom{we have already fixed $m$?} and; e.g. K = C[t,t^{-1}] is not a field!!! 
Consider $ K^m $ as a $K$-module. By restriction $ K^m$ can be viewed as an $R$-module.  An $R$-lattice in $K^m$ 
% \acom{what is $M$? should be $K^m$?}; bc Joel was thinking about arbitrary free modules 
is an $R$-submodule $ L \subset K^m$ such that $ L $ is a free rank $ m $ $R$-module and $ L \otimes_R K = K^m $.  Equivalently, $ L = \Sp_R(v_1, \dots, v_m)$ where $v_1, \dots, v_m$ are free generators of $K^m$. \jcom{Maybe need that both $K$ and $R$ are integral domains and have the same field of fractions?} \acom{Roger proved it.}
% is this true?

% The trivial lattice is 
$L_0 = L_0(R) = R^m \subset K^m $ is called the standard lattice. The group $\GL_m(K) $ acts transitively on the set of $R$-lattices in $K^m$, thus giving a bijection between 
% the set of such lattices 
this set and $\GL_m(K)/\GL_m(R)$. \acom{Maybe abuse notation and warn the reader.}

We will be particularly interested in $\CC[t]$-lattices in $ \CC(t)^m$.  Given such a lattice $ L $ and a point $ a \in \CC$, the specialization of $ L $ at $ a $ is defined as
$$
% L(a) := L \otimes_{\CC[t]} \CC\xt[t-a] \subset \CC\xT[t-a]^m\,.
L(a) := L \otimes_{\CC[t]} \cO_a \subset \cK_a^m\,.
$$
We say that $ L $ is trivial at $ a $ if $ L(a) = \cO_a^m$. 
% \acom{Do we want to employ the notation $\cO_a$ and $\cK_a$ here?}
For example, the lattice $(t-s)^{-1}\CC[t] \subset \CC(t)$ is trivial at any $a\ne s$.

@@

\subsection{Affine Grassmannians} %  actors
% To map thick Gr to C is to map a lattice to the points where it isn't trivialzable; doesn't make sense to ask for poles 
% G(C(t))/G(C[t]) for example lives over the Ran space, finitely many eigenvalues; positive part of thick contains this guy as image 
Set $\AA = \AA^1$.

\begin{itemize}
    \item The ordinary affine Grassmannian $\Gr = G(\cK)/G(\cO)$. It is described in modular terms by 
    $$
    \Gr = \{ (P, \varphi) : \text{$V$ is a rank $m$ vector bundle on $ D_0 $, $\varphi : V \xrightarrow{\sim} V_0 $ on $ D_0 \setminus \{0\} $} \} 
    $$
    where $V_0$ is the trivial rank $m$ vector bundle, and $ D_0$ is the formal disk centered at $ 0 \in \PP$.

    We also have a lattice description 
    $$ 
    \Gr = \{ L \subset \cK^m : \text{ $L$ is a $\cO$-lattice} \}\,.
    $$
    % 
    \item For any $ s \in \CC $, 
    % \acom{should it be $\AA$ instead of $\CC$} 
    the ordinary affine Grassmannian $\Gr_s = G(\cK_s)/G(\cO_s)$ at $ s $. It is described in modular terms by
    $$
    \Gr_s = \{ (P, \varphi) : \text{$V$ is a rank $m$ vector bundle on $ D_s $, $\varphi : V \xrightarrow{\sim} V_0 $ on $ D_s \setminus \{s\} $} \} 
    $$
    where $D_s$ is the formal disk centered at $s$ viewed as an element of $\PP$.

    We also have a lattice description 
    $$ 
    \Gr_s = \{ L \subset \cK_s^m : \text{ $L$ is a $\cO_s$-lattice} \} \,. 
    $$   
    \item The thick affine Grassmannian $\Grth = G(\Kinf)/G(\CC[t])$. % \CC\xT[t^{-1}]
    It is described in modular terms by
    $$
        \Grth = \{ (P, \varphi) : \text{$V$ is a rank $m$ vector bundle on $ \PP $, $\varphi : V \xrightarrow{\sim} V_0 $ on $ D_\infty $ } \} % (a disk centered at $ \infty$)
    $$
    where $D_\infty$ denotes a disk centered at $ \infty$. 
    % \acom{What is the difference between ``a disk'' and ``the formal disk''} \jcom{No difference.}

@@

    % \jcom{Maybe write $\Kinf$ for $ \CC\xT[t^{-1}] $?  Also maybe change the ``thick'' notation''.} \acom{Since $\sf th$ is also the first two letters of ``thin''?} \jcom{That's a good point!  Maybe we could use some kind of bold  Gr (``thick'' letters) or maybe that would be too confusing.} \acom{Ok, it's tentative.}

    \item The (two point) Beilinson--Drinfeld Grassmannian $\pi : \Grbd\to \AA$ (with one point fixed at 0, and the second point $s\in\AA$ varying).
    It is described in modular terms by
    % {\small
    $$
    \Grbd = 
    % \begin{aligned}
        \left\{ 
            (V,\varphi,s) : V\text{ is a rank $m$ vector bundle on }\PP, \varphi : V \xrightarrow{\sim} V_0 \text{ on } \PP \setminus \{0, s\}  
        \right\} 
    % \end{aligned}
    $$%}

    The fibre of $\Grbd \to \AA$ over $ s \in \AA $, for $ s \ne 0$, will be denoted $ \Gr_{0,s} $ and is given by \rcom{why do we have the $s\ne 0$ restriction here}
    % 
    $$ 
    \Gr_{0,s} = G(\CC[t, t^{-1}, (t-s)^{-1}]/G(\CC[t])\,. % := \pi^{-1}(s) 
    $$
    % \acom{0 in notation is kinda redundant? But we can't take it away because we already have a $\Gr_s$ and it is something else?}
    % \jcom{Yes, that is one reason.  But also, there was a comment of yours before in the file, saying that you sometimes got confused that one point was fixed at 0, so this is a good notation to remind us (and the reader).  For the same reason, maybe we should write $ \Gr_{0, \AA}$ instead of $ \Gr_\AA$.}
    % \acom{lol}

    We also have a lattice descriptions 
    % {\small
    \begin{gather*}
    \Grbd = 
    \{ (L,s) :
    % s\in\AA,\,
    % L \subset  \CC(t)^m, s \in \AA 
    \text{$L \subset  \CC(t)^m$ is a $\CC[t]$-lattice trivial at any $ a \ne 0, s$} \} \\
    % , $L$ is 
     \Gr_{0,s} = 
    \{ L \subset  \CC[t,t^{-1},(t-s)^{-1}]^m : \text{ $L$ is a $\CC[t]$-lattice} \}
    \end{gather*}%}
    \acom{We do not consistently specify where $s$ is in these definitions}
    % \acom{$s\in\CC$ should be $s\in\AA$?}
    % \jcom{Sorry I was very consistent about $ \CC$ vs $\AA$.  Which do you prefer?}
    % 
    \item The positive parts $ \Gr^+$ and ${\Grth}^+$ of the affine Grassmannian and of the thick affine Grassmannian resp.\ are defined as 
    % and of the thick affine Grassmannian ${\Grth}^+$ is defined as
    $$
    \Gr^+ = (M_m(\cO) \cap G(\cK)) / G(\cO) \quad {\Grth}^+ = (M_m(\CC[t]) \cap G(\Kinf) / G(\CC[t]) % \CC\xT[t^{-1}] missed a spot  
    $$
    % \acom{What is $M_m$?} \jcom{The space of matrices.  I added it to the beginning of section 2.}

@@

    In lattice terms, $ \Gr^+$ (resp. ${\Grth}^+$) contains those lattices $L$ which are contained in the (relevant?) standard lattice. 
    % \acom{previously called ``trivial''} \jcom{I changed it so that $ R^m $ is called the standard lattice.  But I would like to leave the terminology ``trivial at $ a$'' is that ok, or should we write ``standard at $a$''.} 
    % \acom{Oh, I don't know.. is trivialized at $a$? is standardized at $a$? Maybe standard at $a$ is better.. Man I never thought about this interchangeable lingo.} 
    % lattice $ L_0(\cO)$ (resp. $L_0(\CC[t])$). % , i.e. $ L \subseteq L_0$.
\end{itemize}
% \acom{enumerate the points for now}
These different versions of the affine Grassmannian are related as follows.

\begin{enumerate}
    \item First there is an isomorphism $ \Gr_s \cong \Gr $ coming from the isomorphism $ \cK \cong \Ks$.
    \item Second, we have a map from the two point BD affine Grassmannian to the thick affine Grassmannian $ \Grbd \rightarrow \Grth $
    % $$ \Grbd \rightarrow \Grth $$ 
    which is given in modular terms by restricting the trivialization to $ D_\infty$.  It is given in group-theoretic terms on the fibre over $ s $ by
    $$
    G(\CC[t, t^{-1}, (t-s)^{-1}])/ G(\CC[t]) \rightarrow G(\Kinf)/G(\CC[t])
    $$
    % \acom{Permission to update notation and replace $\CC\xT[t^{-1}]$ by $\Kinf$ as per your suggestion Joel?}
    % \jcom{Permission granted!}
    % \acom{replaced}

    Finally, it is given in lattice terms as the identity on the lattice and using the inclusion $\CC[t, t^{-1}, (t-s)^{-1}]^m \rightarrow \Kinf^m$ on the ambient spaces.
    \item The fibres $ \Gr_{0,s}$ of $ \Grbd \rightarrow \AA$ can be described as % are given as follows
    $$
    \Gr_{0,s} \cong 
    \begin{cases} 
        \Gr \times \Gr_s & s \ne 0 \\
        \Gr              & s = 0\,.
    \end{cases}
    $$
    In the $s\ne 0$ case, the isomorphism is given in the modular realization by restricting the vector bundle and trivializing to the appropriate disks.  
    In the lattice realization, it is given by forming tensor products 
    $$
    L \mapsto (L(0), L(s))\,.
    $$
    % in the $ s \ne 0 $ case.
    \jcom{Maybe we should introduce some notation for this isomorphism.}
    % \acom{Ok. Question: how is the isomorphism given at $s=0$?}
    \acom{Ok. TODO. Also write this in group theoretic terms. Probably $[g] \mapsto ([g],[g])$ is ok. Since $g\CC[t]\otimes_{\CC[t]}\cO_s \cong g\cO_s $ for some reason, where $g\in\CC[t,t^{-1},(t-s)^{-1}]$ can be viewed as $g\in\cK_s$.}

@@

    \jcom{I tried to answer your question, but didn't explain it well.  When $ s = 0$, the map is the same except that $ L(0) = L(s) $ , so we only need $L(0)$.}
\end{enumerate}

\subsection{The fusion construction}
The following construction will be very important in this paper.  Let $ X_1, X_2 \subset \Gr$ be two subschemes. Then using the isomorphism $ \Gr \cong \Gr_s $, for each $ s $, we obtain a subscheme $ X_1 \times X_2 \subset \Gr \times \Gr_s $.  
% <<<<<<< HEAD
% Via \ul{this} \acom{rather, the above? $L\mapsto (L(0),L(s))$} 
Next, using the isomorphism $ \Gr_{0,s} \cong \Gr \times \Gr_s $, 
for each $ s \ne 0$,  
\rcom{usually written $\Gr_{0,\AA^\times} \cong \Gr \times \Gr_s \times \AA^\times$, cite MVi} 
we obtain a subscheme $ X_1 \times X_2 \times \AA^\times $  of $\Grbd$.  
% =======
% Via the isomorphism $ \Gr_{0,s} \cong \Gr \times \Gr_s $,  for each $ s \ne 0$, we obtain a subscheme $ X_1 \times X_2 \times \AA^\times $  of $\Grbd$.  
% >>>>>>> 5a15ce15b14109bab482282aa5657c9596f7892d

@@

\acom{We will write only coset representatives for (orbits of) elements of the various Grassmannians; right cosets will be clear from context.}

% 
\begin{itemize}
    % \item Weights $\mu_i\le\lambda_i$ of size $N_i$ ($i=1,2$) 
    % \item Their sums $\mu = \sum \mu_i \le \lambda = \sum\lambda_i$ of size $N = \sum N_i$
    \item The lattice $L_\lambda$ corresponding to the point $t^\lambda\in\Gr$. 
    % In the lattice model, we have %  G(\cO); understood from context 
    $$ 
    L_\lambda = \Sp_\cO(t^{\lambda_1}e_1, \dots, t^{\lambda_m}e_m)\,. 
    $$ 
    \item The orbit $\Gr^\lambda = G(\cO) L_\lambda$ and its closure 
    $ \overline\Gr^\lambda = \bigcup_{\lambda' \le \lambda} \Gr^{\lambda'} $.  
    \acom{do we prefer $\overline{\Gr}^\lambda$ to $\overline{\Gr^\lambda}$? I am for the former! Though it is less accurate??} \jcom{I'm not sure which is better.  I was ``testing'' it out.}
    This orbit lies inside the positive part $ \Gr^+$ of the affine Grassmannian.
    % 
    \item The family $ \overline{\Gr}_{0,\AA}^{\lambda_1, \lambda_2} \rightarrow \AA$ defined by $ \overline{\Gr}^{\lambda_1, \lambda_2}_{0, \AA} = \overline{\Gr}^{\lambda_1} \ast_\AA \overline{\Gr}^{\lambda_2}$. 
    % \acom{I guess that it is good to have the notation here, in place of $\overline{\overline\Gr^{\lambda_1}\times\overline\Gr^{\lambda_2}\times\AA^\times}$..}
    %\acom{should we also subsript this family with $0,\AA$?}

@@

    Suppose that $ s \ne 0$.  In the fibre $\overline{\Gr}_{0,s}^{\lambda_1, \lambda_2}$ we have the open locus $ \Gr_{0,s}^{\lambda_1, \lambda_2}$ coming from transporting $ \Gr^{\lambda_1} \times \Gr^{\lambda_2} $ via the isomorphism $ \Gr_{0,s} \cong \Gr \times \Gr_s $.  This open locus is a $ G(\CC[t])$-orbit
    % .  The lattice description of $ \Gr_{0,s}^{\lambda_1, \lambda_2}$ 
    whose lattice description is given in \Cref{le:Grl1l2} below.
    \acom{Why $G(\CC[t])$. Because we are on the left side!}

    \item The locus $\cW_\mu = G_1\xt[t^{-1}]L_\mu \subset \Grth $.  
    \acom{want $t^\mu\CC[t]$ as opposed to $L_\mu$ here? Use thick $L_0$, $L_\mu$. $t\in R$, $t^\mu L_0(R)$. Or just use $t^\mu$.}
    In modular terms, this corresponds to the locus of those $ (V, \varphi)$ such that $ V $ is isomorphic to the trivial vector bundle on $ \PP$ and such that $ \varphi$ preserves the {Harder--Narasimhan filtration of $V$ at $ \infty$}.  The lattice description of $ \cW_\mu \cap \Grth^+$ is given in Lemma \ref{le:Wmu} below.
